The contact value approximation for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-03-24 papers/pair-correlation/paper.tex
updates to pair paper Tested on bennet. Took 0:21.45.

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We have developed an approximation for the pair distribution
  function of hard spheres, which is based on the average value of the
  pair distribution function at contact we recently developed.  Our
  pair distribution function is constructed so as to be computable
  with only single-site convolutions and to accurately reproduce the
  averaged distribution function at contact.  This results in a
  functional that is efficient to compute, and predicts the pair
  distribution function as well as the most accurate existing
  analytical approximation.  \fixme{needs special attention.}
  \fixme{add acronym, and discuss separable vs. non}
\end{abstract}

@@

The standard approach in liquid state theory is to model a liquid as a
hard-sphere reference fluid with attractive interactions that are
treated perturbatively~\cite{hansen2006theory}.  Recent advances have
extended these perturbative approaches to inhomogeneous density
distributions---that is, liquid interfaces---through the use of
classical density functional theory (DFT), in which the grand free
energy is found by minimizing a free energy functional of the
density~\cite{ jain2007modified, gloor2007prediction,
  gross2009density,
  %felipe2001examination, gloor2002saft,
  %gloor2004accurate, clark2006developing,
  kahl2008modified,
  % yu2002fmt-dft-inhomogeneous-associating,
  %fu2005vapor-liquid-dft, bryk2006density,
  hughes2013classical,
  %segura1998comparison, felipe2001examination,
  %gloor2002saft, gloor2004accurate, fu2005vapor-liquid-dft,
  bryk2006density, clark2006developing,
  kahl2008modified, gross2009density,
  %yu2002fmt-dft-inhomogeneous-associating,
  sundararaman2012computationally, marshall2013density}.  The
perturbation theory treatment of intermolecular interactions relies on
the pair distribution function of the reference fluid:
$g^{(2)}(\rr_1,\rr_2)$.  Unlike the radial distribution function of a
homogeneous fluid, there does not currently exist a tractable form for
the pair distribution function of an inhomogeneous hard-sphere fluid,
suitable for use in constructing a density
functional~\cite{gloor2007prediction, jain2007modified}.

>>>>

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We have developed an approximation for the pair distribution
  function of hard spheres, which is based on the average value of the
  pair distribution function at contact we recently developed.  Our
  pair distribution function is constructed so as to be computable
  with only single-site convolutions and to accurately reproduce the
  averaged distribution function at contact.  This results in a
  functional that is efficient to compute, and predicts the pair
  distribution function as well as the most accurate existing
  analytical approximation.  \davidsays{Jeff will rewrite this
    abstract.}
\end{abstract}

@@

\davidsays{Everyone reads a print copy of the the paper by Tuesday
  evening.  Then Paho submits!}

\davidsays{Paho volunteered to check over and figure out what to do
  with the $HS$ in $g$.  Can we get away with $HS$ everywhere?
  Defining two macros so that we can go back and forth.}

The standard approach in liquid state theory is to model a liquid as a
hard-sphere reference fluid with attractive interactions that are
treated perturbatively~\cite{hansen2006theory}.  Recent advances have
extended these perturbative approaches to inhomogeneous density
distributions---that is, liquid interfaces---through the use of
classical density functional theory (DFT), in which the grand free
energy is found by minimizing a free energy functional of the
density~\cite{ jain2007modified, gloor2007prediction,
  gross2009density,
  %felipe2001examination, gloor2002saft,
  %gloor2004accurate, clark2006developing,
  kahl2008modified,
  % yu2002fmt-dft-inhomogeneous-associating,
  %fu2005vapor-liquid-dft, bryk2006density,
  hughes2013classical,
  %segura1998comparison, felipe2001examination,
  %gloor2002saft, gloor2004accurate, fu2005vapor-liquid-dft,
  bryk2006density, clark2006developing,
  kahl2008modified, gross2009density,
  %yu2002fmt-dft-inhomogeneous-associating,
  sundararaman2012computationally, marshall2013density}.  The
perturbation theory treatment of intermolecular interactions relies on
the pair distribution function of the reference fluid:
$g_{HS}^{(2)}(\rr_1,\rr_2)$.  Unlike the radial distribution function of a
homogeneous fluid, there does not currently exist a tractable form for
the pair distribution function of an inhomogeneous hard-sphere fluid,
suitable for use in constructing a density
functional~\cite{gloor2007prediction, jain2007modified}.
